Effects of pulsed hollow electron lens operation on the beam core in HL-LHC: \\First experimental studies and simulations.

### 2018-01-17 resex.tex
add Daniels part

\subsection{Excitation with transverse damper and filling scheme\label{sec:adt}}
\textcolor{red}{Daniel's part}
\begin{itemize}
	\item error on amplitude
	\item synchronization of H and V kicker
	\item random noise on amplitude - is there any?
	\item bandwidth - why does the damper not affect the nth turn pulsing????
	\item filling scheme
\end{itemize}

>>>>

\subsection{Excitation with transverse damper and filling scheme\label{sec:adt}}
The primary function of the transverse feedback system in LHC (also referenced to as ADT) is to provide injection oscillation damping and actively damp the coupled bunch instabilities driven by the machine impedance. The main building blocks of the ADT system are stipline pickups at the position Q7 and Q9 at Point 4 of the LHC, connected to the beam position measurement modules at the surface, the digital signal processing modules (mDSPU) and a set of tetrode power amplifiers feeding electrostatic kickers in the RF zone of LHC \cite{}.

Though originally designed to damp the undesired transverse activities only, thanks to the state of the art digital signal processing hardware the damper is being routinely used for sophisticated beam excitations as well (e.g. Abort gap and injection gap cleaning, single bunch excitation for tune and linear coupling measurements, machine development etc.).

The transverse feedback is active during the whole LHC cycle, therefore it is of very high importance, that the noise introduced by the system does not contribute to any emittance growth. The typical machine cycle requires a short damping time of ~10-20 turns (high feedback gain) for injection oscillation damping, which is increased during the ramp and stable beams to ~50-100 turns (lower feedback gain). It had been demonstrated that noise introduced by the transverse feedback system itself is sufficiently low to introduce any measurable emittance growth \cite{}. All excitation signals referenced to in this paper, are digitally synthesized in the damper's digital signal processing units and therefore can be considered as ``noise-free''.

The resonant excitation experiment involved simultaneous measurements on three groups of 72 bunches with a dedicated excitation pattern and transverse feedback configuration on each sub-group of 6 bunches as shown in Fig.~\ref{fig:fill}.
\begin{figure*}
		\centering
		\includegraphics[width=1.0\linewidth]{bunchfilling.png}	
	\caption{\label{fig:fill} Filling and excitation scheme for LHC experiments in 2017.}
\end{figure*}

The excitation in the horizontal and the vertical plane is generated by a different set of signal processing hardware, however during this experiment the signals were synchronized at a turn level. This means the bunches of the third group (of 72 bunches) experienced the kick in both horizontal and vertical plane during the same turn.

Fig.~\ref{fig:fill_meas} shows the oscillation amplitude of each bunch in both H and V planes captured by the LHC real time transverse activity monitor. The measured activity is well in line with the expected excitation pattern.
\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{bunchfilling_measured.png}	
	\caption{\label{fig:fill_meas} Excitation amplitude in horizontal and vertical measured during the 2017 experiment during the $8^{\mathrm{th}}$~turn pulsing.}
\end{figure}

\begin{itemize}
	\item error on amplitude \textcolor{red}{missing}
	\item synchronization of H and V kicker \textcolor{green}{done}
	\item random noise on amplitude - is there any? \textcolor{green}{done}
	\item bandwidth - why does the damper not affect the nth turn pulsing???? \textcolor{red}{missing}
	\item filling scheme \textcolor{green}{done for 2017}, \textcolor{red}{missing for 2016}
\end{itemize}
